intRo

### 2016-06-24 jcgs-paper-2016/response.Rmd

P 5: Fig 2 shows a simple design that should be easy for casual users (as intro students really are) to get their heads around. Not all that keen on the use of “statistics” as a category heading in Panel 2 because it reinforces the ghettoizing of the word conflicting with a message that says everything you are doing here is statistics.

**We have updated the application (and the screenshot) to refer to the contingency, regression, and t-test modules category heading as "inference" rather than "statistics", to help emphasize that numerical and graphical summaries are also statistics.**

P 6 top: When you look at the actual R code generated it can be quite complex with its pipe structures etc which I would have thought does rather limit its introductory value.

**We appreciate the comment. In teaching R Workshops at Iowa State, we observed that among many of the introductory R students we encountered, the pipe structure was often preferred to using traditional nested function calls. The pipe structure is also the standard by which `ggvis` plots are created, which we are using as the backend to our graphical module. We do understand, however, that certain instructors may wish to include a modified version of the default modules removing the piping, which by following the procedure described in the paper would be a relatively simple task.**

### 2016-06-28 user-2016/index.Rmd
changed a word

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP`, `Deducer`, `Rcmdr` are powerful, but too big
      - Licenses and inconsistent UI
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software

>>>>

 - `R` is great, but requires students to have some knowledge/interest in programming
 - `JMP`, `Deducer`, `Rcmdr` are powerful, but too big
      - Licenses and installation
 - New tools recently released to spark an interest in `R`
      - `Swirl` and DataCamp teach `R` programming
      - Project MOSAIC facilitates learning, but assumes knowledge of `R`
 - Want students to focus on data analysis rather than fight with software
